The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-12-01 manuscript/manuscript.qmd
Start streamlining theory section

Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus. Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018]. INGOs that are unable to find a PSU willing to support their proposed programming are unable to work in the country. The mechanisms of the ONGO Law thus provide the government with latitude to selectively partner with INGOs that align with regime preferences while providing layers of oversight and control.

@@

@@

@@

In 2018 Batke and Hang posited that the ONGO law was showing signs of reorienting the missions of legally recognized INGOs and the overall scope of international civil society to be more explicitly aligned with government preferences. @HolbigLang:2022 recently confirmed this prediction, finding that the issue areas addressed by legally recognized INGOs have "shift\[ed\] towards fields of activity high up the government's domestic policy agenda" [-@HolbigLang:2022, p. 587].

@@

As seen previously, INGOs must partner with professional supervisory units (PSUs) to become ROs. Organizations vary in their ability to attract partner PSUs, and INGOs that are unable to find corresponding PSUs are more limited in their geographic reach within the country. INGOs are authorized to operate within China on a province-by-province basis. Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province. We use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020]. For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service. Having the potential to shift programs to other provinces as needed thus provides a form of operational space.

@@

Our final independent variable measures how much time elapsed between the January 1, 2017 (when the law took effect) and the organization's official registration date. There is great variance in the timing of registering an RO among INGOs, since there has been a *de facto* grace period for INGOs to seek legal presence after the law took effect[@Shieh:2018]. This is largely because both INGOs and the regulators needed some transitional time to explore the specific implementation of the law as large ambiguity was left when the law was passed. We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register an RO, for some INGOs are inclined to avoid the cumbersome registration procedures at the early stage if there is no real consequences for continuing operations without registration, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic. (TODO: find a citation for this, probably Spires, if there is one.)

@@

@eq-ordbeta provides a formal definition of our modeling choices. Since we are primarily interested in how an INGO's issue area, its local connections, and the timing of its registration after January 2017, we include these as explanatory variables. We also include province-specific random offsets for each intercept to account for between-region differences in how INGOs are regulated, since every RO is overseen by provincial-level Public Security Bureaus. We use weakly informative priors for all model parameters.

::: column-page-inset
$$
\begin{aligned}
&\ \textbf{Registered provinces for INGO } i \\
\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_i, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
&\ \textbf{Model of outcome average} \\
% Put the huge equation in a nested \begin{aligned}[t] environment so that 
% \mathrlap{} can go around it so that the annotations in the priors can be 
% aligned closer to the math
\mu_i =&\ 
  \mathrlap{\begin{aligned}[t]
  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
  & \beta_{11}\ \text{Time since January 2017} + \beta_{12}\ \text{Year registered}
  \end{aligned}}\\[8pt]
&\ \textbf{Priors} \\
\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
\end{aligned}
$$ {#eq-ordbeta}
:::

@@

>>>>

Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental unit related to an INGO's issue area which oversees and co-supervises the INGO with Public Security Bureaus. Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, since potential PSUs do not have a legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018].

Organizations vary in their ability to attract partner PSUs, and INGOs that are unable to find corresponding PSUs are more limited in their geographic reach within the country. INGOs are authorized to operate within China on a province-by-province basis. Many organizations are allowed to work in all 32 mainland provincial administrative regions, but many are also only authorized to work in a handful, or even only a single province. In this paper, we use the number of provinces that INGOs are authorized to work in as a proxy for INGO operational space based on the assumption that INGOs need to or hope to be able to carry out their programs in as broad a geographical scope as possible [@Li:2020]. For example, in emergency circumstances like the COVID-19 pandemic, it would be extremely difficult for INGOs to plan beforehand which areas might need their service. Having the potential to shift programs to other provinces as needed thus provides a form of operational space.

@@

In 2018, @BatkeHang:2018 posited that the ONGO law was showing signs of reorienting the missions of legally recognized INGOs and the overall scope of international civil society to be more explicitly aligned with government preferences. @HolbigLang:2022 recently confirmed this prediction, finding that the issue areas addressed by legally recognized INGOs have "shift\[ed\] towards fields of activity high up the government's domestic policy agenda" [-@HolbigLang:2022, p. 587].

@@

Operational space is determined by the interaction between NGO characteristics and regime preferences

@@

@@

As seen previously, INGOs must partner with professional supervisory units (PSUs) to become ROs. TODO describe the province count variable

@@

Our final independent variable measures how much time elapsed between the January 1, 2017 (when the law took effect) and the organization's official registration date. There is great variance in the timing of registering an RO among INGOs, since there has been a *de facto* grace period for INGOs to seek legal presence after the law took effect [@Shieh:2018]. This is largely because both INGOs and the regulators needed some transitional time to explore the specific implementation of the law as large ambiguity was left when the law was passed. We use this temporal variable as a proxy for the motivation or eagerness of INGOs to register an RO, for some INGOs are inclined to avoid the cumbersome registration procedures at the early stage if there is no real consequences for continuing operations without registration, while others took the time to talk with multiple potential PSUs to find a more suitable superior or regulatory dynamic. (TODO: find a citation for this, probably Spires, if there is one.)

@@

Since we are primarily interested in how an INGO's issue area, its local connections, and the timing of its registration after January 2017, we include these as explanatory variables. We also include random province intercepts to account for between-region differences in how INGOs are regulated, since every RO is overseen by provincial-level Public Security Bureaus. We use the following model and priors (see appendix TODO for more details):

$$
\begin{aligned}
&\ \textbf{Registered provinces for INGO } i \\
\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_i, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
&\ \textbf{Model of outcome average} \\
\mu_i =&\ 
  \mathrlap{\begin{aligned}[t]
  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
  & \beta_{11}\ \text{Time since January 2017} + \beta_{12}\ \text{Year registered}
  \end{aligned}}\\[8pt]
&\ \textbf{Priors} \\
\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
\end{aligned}
$$

@@

\newpage

:::: {#appendix-count}

# Appendix

::::
